Icicle: write once, run once

### 2016-05-28 2016fhpc/section/04-Benchmarks.tex
benchmarks

\caption{Throughput comparisons of Icicle against existing R code and standard Unix utilities}
\label{fig:bench:other}
\end{figure}

@@

\begin{tikzpicture}
\begin{axis}[
	x tick label style={/pgf/number format/1000 sep=},
	ylabel=MB/s,
  ymin=800, ymax=1100,
%  xmax=372,
  xlabel=Number of queries,
	enlargelimits=0.01,
	legend style={legend columns=-1},
%	legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
%	ybar interval=0.7,
]

% bench/raw.txt
% Running with fewer queries
 \addplot coordinates {(0,1025.5) (1,1029.6) (48,978) (96,941) (144,943) (192,936) (240,904) (276,895.5) (324,881) (372,846.2) };

@@

\legend{CSE, No CSE, dev/null};

@@

\caption{Decrease in throughput as queries are added, with and without common subexpression elimination (CSE) over queries}
\label{fig:bench:queries}
\end{figure}

@@

Figure~\ref{fig:bench:queries} shows how Icicle scales in throughput as more queries are added.

>>>>

\caption{Throughput comparisons of Icicle against existing R code and standard Unix utilities; higher is faster.}
\label{fig:bench:other}
\end{figure}

@@

\begin{tikzpicture}
\begin{axis}[
	x tick label style={/pgf/number format/1000 sep=},
	ylabel=MB/s,
  ymin=0, ymax=1200,
%  xmax=372,
  xlabel=Number of queries,
	enlargelimits=0.01,
	legend style={legend columns=-1},
%	legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
%	ybar interval=0.7,
]

% bench/raw.txt
% Running with fewer queries
% \addplot coordinates {(0,1025.5) (1,1029.6) (48,978) (96,941) (144,943) (192,936) (240,904) (276,895.5) (324,881) (372,846.2) };

@@

% No fusion, no output
% \addplot coordinates { (0,987) (31,1037) (62,1024) (93,1002) (124,1037) (155,1024) (186,1004) (217,1040) (248,1023) (279,998) (310,1018) (341,1013) (372,1003) };

\legend{Output to disk, Output to /dev/null};

@@

\caption{Decrease in throughput as queries are added. By comparing writing the output to disk and writing to /dev/null, we see that actual computation time remains constant.}
\label{fig:bench:queries}
\end{figure}

@@

Figure~\ref{fig:bench:queries} shows how Icicle scales in throughput as more queries are added.
We ran with a number of queries twice, with one version writing output to disk, and the other throwing away the result to @/dev/null@ rather than spending time writing.
The graph shows the disk version decreasing roughly linearly in the number of queries, while ignoring the output stays constant.
This suggests that the output code is the bottleneck, which is unsurprising given the output format is text-based PSV.
The upshot of this is that the time spent computing the queries appears constant as hundreds of queries are added, which suggests that many more queries can be handled.
